---
title: "Access policy brief"
format: {html: {toc: true, embed-resources: true}}
execute: {echo: true, warning: false, message: false}
---

## Question

Which economies closed the combined electricity and internet access gap fastest between 2000 and 2022?

## Data, unit, and plan

One row represents one economy with observed endpoints in 2000 and 2022. Changes are percentage-point differences. The combined measure gives equal weight to electricity and internet access.

```{r}
library(tidyverse)
access <- read_csv("../../data/lesson-4/access-2000-2022.csv", show_col_types = FALSE)
glimpse(access)
```

## Briefing table

Show the ten economies with the largest combined gap closure. Retain the separate electricity and internet changes so the index remains interpretable.

```{r}
# Use arrange() and slice_head(). Select the columns a reader needs.
```

## Figure

Plot the electricity change against the internet-use change. Map region to color and add horizontal and vertical reference lines at zero.

```{r}
# Use ggplot(), geom_point(), geom_hline(), geom_vline(), and labs().
```

## Finding

Write one numerical finding about the joint change and its two components.

## Limitation

Explain one consequence of the equal-weight index or endpoint comparison.

## AI use and verification

After saving your independent work, use the prompt in the handout. Record the claim you checked, your independent R evidence, and your decision: accept, revise, or reject.
