---
title: "Climate policy brief"
format: {html: {toc: true, embed-resources: true}}
execute: {echo: true, warning: false, message: false}
---

## Question

Which economies expanded renewable electricity, reduced carbon intensity, and ended with higher real income between 2000 and 2021?

## Data, unit, and plan

One row represents one economy with all six endpoint measures observed. The income result compares endpoints; it does not mean income rose in every intervening year.

```{r}
library(tidyverse)
climate <- read_csv("../../data/lesson-4/climate-2000-2021.csv", show_col_types = FALSE)
glimpse(climate)
```

## Briefing table

Count qualifying economies by region, then list the qualifying economies with the largest renewable-electricity gains.

```{r}
# Filter transition == TRUE. Then group_by()/summarise() or arrange().
```

## Figure

Plot renewable-electricity change against carbon-intensity percent change. Map income percent change to color and add reference lines at zero.

```{r}
# Build the quadrant figure with ggplot(), geom_point(), reference lines, and labs().
```

## Finding

Write one numerical finding about the endpoint rule.

## Limitation

Explain why coexistence of the three changes does not identify a policy cause or continuous growth path.

## AI use and verification

After saving your independent work, use the prompt in the handout. Record the claim you checked, your independent R evidence, and your decision: accept, revise, or reject.
