---
title: "Gender policy brief"
format: {html: {toc: true, embed-resources: true}}
execute: {echo: true, warning: false, message: false}
---

## Question

Where is girls' secondary enrollment associated with lower adolescent fertility in 2022, and where does the pattern depart from the overall comparison?

## Data, unit, and plan

One row represents one economy in 2022. Gross enrollment can exceed 100 by definition. Before coding, write the variables and function sequence you will use.

```{r}
library(tidyverse)
gender <- read_csv("../../data/lesson-4/gender-2022.csv", show_col_types = FALSE)
glimpse(gender)
```

## Briefing table

Construct one row per region. Report the number of economies and the median of each measure. Arrange by median adolescent fertility.

```{r}
# Use group_by(), summarise(), and arrange().
```

## Figure

Plot female secondary enrollment against adolescent fertility. Map region to color and label both measures with their documented units.

```{r}
# Build the plot with ggplot(), aes(), geom_point(), and labs().
```

## Finding

Write one numerical finding that distinguishes the overall pattern from regional variation.

## Limitation

State one limitation arising from coverage, measurement, or interpretation.

## AI use and verification

After saving your independent work, use the prompt in the handout. Record the claim you checked, your independent R evidence, and your decision: accept, revise, or reject.
