---
title: "Health policy brief"
format: {html: {toc: true, embed-resources: true}}
execute: {echo: true, warning: false, message: false}
---

## Question

How is national income associated with under-five mortality in 2022, and how does the pattern differ by current income group?

## Data, unit, and plan

One row represents one economy in 2022. Before coding, write the variables and the function sequence you will use.

```{r}
library(tidyverse)
health <- read_csv("../../data/lesson-4/health-2022.csv", show_col_types = FALSE)
glimpse(health)
```

## Briefing table

Construct one row per current income group. Report the number of economies, median GDP per capita (PPP), and median under-five mortality. Arrange the result by median mortality.

```{r}
# Begin with health |>, then use group_by(), summarise(), and arrange().
```

## Figure

Plot GDP per capita against under-five mortality. Map current income group to color and use a logarithmic x-axis.

```{r}
# Begin with ggplot(). Add geom_point(), scale_x_log10(), and labs().
```

## Finding

Write one numerical finding that names the year, sample, and units.

## Limitation

State one inference this cross-section does not support.

## AI use and verification

After saving your independent work, use the prompt in the handout. Record the claim you checked, your independent R evidence, and your decision: accept, revise, or reject.
