---
title: "Income and under-five mortality"
subtitle: "Lesson 4 demonstration brief"
format:
  html:
    toc: true
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Question

How is national income associated with under-five mortality in 2022, and how does the pattern differ across current income groups?

## Data and sample

The file contains one row per economy in 2022. The analytical sample includes the 120 economies with GDP per capita, PPP, above $10,000 and observed under-five mortality.

```{r}
library(tidyverse)

health <- read_csv(
  "../data/lesson-4/health-2022.csv",
  show_col_types = FALSE
)

health_focus <- health |>
  filter(gdp_per_capita_ppp > 10000)

glimpse(health_focus)
```

## Briefing table

```{r}
health_table <- health_focus |>
  group_by(income_level_current) |>
  summarise(
    economies = n(),
    min_mortality = min(under5_mortality),
    average_mortality = mean(under5_mortality),
    median_mortality = median(under5_mortality),
    max_mortality = max(under5_mortality),
    .groups = "drop"
  ) |>
  arrange(median_mortality)

health_table
```

## Figure

```{r}
ggplot(
  health_focus,
  aes(
    x = gdp_per_capita_ppp,
    y = under5_mortality,
    color = income_level_current
  )
) +
  geom_point(alpha = 0.75) +
  scale_x_log10(labels = scales::label_number()) +
  labs(
    x = "GDP per capita, PPP (log scale)",
    y = "Under-five deaths per 1,000 live births",
    color = "Current income group",
    caption = "Source: World Bank, World Development Indicators."
  ) +
  theme_minimal()
```

## Finding

Median under-five mortality is lower in higher-income groups. The figure also shows substantial variation within income groups. This is a descriptive cross-sectional association.

## Limitation

The sample excludes economies missing either measure, the income classification is current metadata, and the comparison does not identify a causal effect of income.

## AI use and verification

After writing the table, figure, finding, and limitation, an agent may reproduce the table and challenge one statement. Record the statement checked, the independent R evidence, and whether you accepted, revised, or rejected the suggestion.
