---
title: "Math Camp field notebook"
subtitle: "Question, code, evidence, judgment"
format:
  html:
    toc: true
    code-fold: false
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Policy question

Write one descriptive or associational question. Name the population, outcome, comparison, and time period.

## Data and definitions

- **Source:** World Bank World Development Indicators
- **Retrieval or snapshot date:**
- **Unit of observation:** country-year
- **Indicators and units:**
- **Known limitations:**

```{r}
#| label: setup

library(tidyverse)

wdi <- read_csv(
  "../data/derived/math-camp-wdi-2000-2022.csv",
  show_col_types = FALSE
)
```

## First inspection

Before using an agent, predict what each check should reveal.

```{r}
#| label: inspect

glimpse(wdi)
count(wdi, year)
summarise(wdi, economies = n_distinct(iso3c))
```

## Analysis sample

Explain every filter and transformation in plain language.

```{r}
#| label: build-analysis-sample

# Replace this example with the variables for your selected policy track.
analysis_data <- wdi |>
  select(iso3c, country, year, income_level_current,
         gdp_per_capita_ppp, under5_mortality) |>
  filter(
    year >= 2000,
    !is.na(gdp_per_capita_ppp),
    gdp_per_capita_ppp > 0,
    !is.na(under5_mortality)
  ) |>
  mutate(log_income = log(gdp_per_capita_ppp))

stopifnot(
  !anyDuplicated(analysis_data[c("iso3c", "year")])
)
```

## Comparison

```{r}
#| label: figure
#| fig-cap: "Replace this caption with the population, variables, years, and units."
#| fig-alt: "Scatterplot of log GDP per capita and under-five mortality for complete country-year observations."

ggplot(analysis_data, aes(log_income, under5_mortality)) +
  geom_point(alpha = 0.4, na.rm = TRUE) +
  labs(
    x = "Log GDP per capita, PPP",
    y = "Under-five deaths per 1,000 live births"
  ) +
  theme_minimal()
```

Write the strongest descriptive or associational statement supported by the output.

## Simple model and interpretation

The coefficient on `log_income` is not the change associated with a one-percent
increase. Translate it into changes that a reader can recognize.

```{r}
#| label: model

fit <- lm(
  under5_mortality ~ log_income + income_level_current,
  data = analysis_data
)

beta <- unname(coef(fit)[["log_income"]])
tibble(
  comparison = c("10% higher GDP per capita", "double GDP per capita"),
  estimated_change_in_deaths_per_1000 = c(
    beta * log(1.10),
    beta * log(2)
  )
)
```

Write both interpretations as pooled associations, comparing observations in
the same included current income-level category. Do not describe either number
as the effect of making a country richer.

## Residual check

```{r}
#| label: residuals

diagnostics <- analysis_data |>
  mutate(
    fitted = predict(fit),
    residual = resid(fit)
  ) |>
  arrange(desc(abs(residual)))

diagnostics |>
  select(country, year, under5_mortality, fitted, residual) |>
  slice_head(n = 8)
```

Choose one row. Record what you checked before proposing a substantive story
for why its observed value differs from the fitted value.

## What this does not show

Name at least one limitation related to measurement, missingness, comparison, or causal interpretation.

## AI-use note

I used **[Codex / Claude Code / other]** to **[explain, generate, debug, review, or update]**. I provided it with **[public project context]**. I verified its contribution by **[tests, source comparison, clean render, or manual review]**. I revised or rejected **[important example]**. I remain responsible for the analysis and interpretation.

## Verification record

| Agent claim or change | Check performed | Result |
|---|---|---|
|  |  | Confirmed / contradicted / unresolved |

## Clean-session receipt

Restart R, choose **Session → Restart R**, then render this notebook without
running chunks manually. Record:

- render date and time;
- R version from `R.version.string`;
- number of model observations from `nobs(fit)`;
- whether the HTML opened without an error;
- any warning you investigated rather than suppressed.

## Handoff checklist

- [ ] The question names a population, outcome, comparison, and period.
- [ ] The data source, snapshot, unit, and indicator definitions are visible.
- [ ] Every object is created before it is used.
- [ ] The figure has units and useful alternative text.
- [ ] The 10% and doubling interpretations match the logged predictor.
- [ ] A residual or other diagnostic is inspected.
- [ ] The claim is associational and a specific limitation is stated.
- [ ] AI assistance and human verification are disclosed.
- [ ] The notebook renders from a clean R session.
